`r params$doc_title`

### 2022-12-03 scripts/MSc.Rmd
raincloud plot added

>>>>

```{r simulated-pves-raincloud-plot}
ggplot(plot_data1b, aes(x=n, y=value, col=name))+    # plot_data1b from section Simlating on empirical data (PVE)
  geom_point(alpha=0.6)+
  geom_line(alpha=0.6)+
  geom_line(aes(x=n, y=count_IVs_scaled, col="Number of IVs"), linetype="dotdash")+
  scale_x_continuous(name = paste0("Size of sample ", as.roman(1)),  # 2-sample-MR or label "Study Size"
                     labels = comma, 
                     breaks = N_annotation, #c( 10000, n[7:length(n)]),
                     #limits = c(10000, 300000)  # throws an error when used with ggdist -> use coord_cartesian() instead!
                     )+
  #ylab("% variance explained by IVs")+
  labs(title = "PVE with simulation added",
       col='', 
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
  ) +
  scale_y_continuous(
    # Features of the first axis
    name = "% variance explained by IVs",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
    limits = c(0,10)
  ) + 
  ## Rainclouds
  # https://z3tt.github.io/Rainclouds/
  # exposure simulation
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, # *100 to get percent values
                                               group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2, outlier.shape = NA)+
  ggdist::stat_halfeye(data = boxplot_overlay_dat, mapping=aes(x=sample_size_filtered, y=value_X*100, group=sample_size_filtered), 
                       inherit.aes = FALSE, 
                       slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                       geom = "slabinterval",
                       na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
  gghalves::geom_half_point(
    data = boxplot_overlay_dat, mapping=aes(x=sample_size_filtered-2000, y=value_X*100, group=sample_size_filtered), 
    inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
    side = "l", range_scale = .4, alpha = .2)+
  # outcome simulation
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_Y*100, # *100 to get percent values
                                               group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[4,2][[1]],
               alpha=0.2, size=0.2, outlier.shape = NA)+
  ggdist::stat_halfeye(data = boxplot_overlay_dat, mapping=aes(x=sample_size_filtered, y=value_Y*100, group=sample_size_filtered), 
                       inherit.aes = FALSE, 
                       slab_fill=ggthemes_data$few$colors$Dark[4,2][[1]], slab_alpha = 0.2,
                       geom = "slabinterval",
                       na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
  gghalves::geom_half_point(
    data = boxplot_overlay_dat, mapping=aes(x=sample_size_filtered-2000, y=value_Y*100, group=sample_size_filtered), 
    inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[4,2][[1]],
    side = "l", range_scale = .4, alpha = .2)+
  coord_cartesian(xlim=c(10000, 300000))+
  theme_few()+
  #scale_colour_few() +
  #scale_color_manual(name = "", values = c("% var(U)" = "red", 
  #                                         "% var(X)" = "blue", 
  #                                         "% var(Y)" = "darkblue", 
  #                                         "Number of IVs" = "black"
  #                                         ))
  #
  scale_color_manual(name = "", values = c("% var(U)" = ggthemes_data$few$colors$Dark[2,2][[1]], 
                                           "% var(X)" = ggthemes_data$few$colors$Dark[3,2][[1]], 
                                           "% var(Y)" = ggthemes_data$few$colors$Dark[4,2][[1]], 
                                           "Number of IVs" = "black"),
                     # order
                     breaks = c( "Number of IVs", "% var(X)", "% var(Y)", "% var(U)")
  ) -> plot_pve_simulated.raincloud
